dispRity manual

### 2017-01-18 doc/dispRity-manual.Rmd
Updated links in manuals

For more information on the metrics, please refer to the [`dispRity` metric manual](https://github.com/TGuillerme/dispRity/blob/master/doc/dispRity-metric.Rmd) for the vignette about the metric implementation in `dispRity`.

@@

The `dispRity` algorithm decomposes the metrics functions into three levels that correspond to the dimensions of the output of each metric function.
For more details on this algorithm please refer to the [metric vignette](https://github.com/TGuillerme/dispRity/blob/master/doc/dispRity-metric.Rmd).

@@

#### `sim.morpho`
This function (and it's associated utilities) allows to generate realistic discrete morphological matrices.
See the [associated vignette](https://github.com/TGuillerme/dispRity/blob/master/doc/dispRity-simulate_data.Rmd) for more details.

>>>>

For more information on the metrics, please refer to the [`dispRity` metric manual](http://htmlpreview.github.com/?https://github.com/TGuillerme/dispRity/blob/master/doc/dispRity-metrics.html) for the vignette about the metric implementation in `dispRity`.

@@

The `dispRity` algorithm decomposes the metrics functions into three levels that correspond to the dimensions of the output of each metric function.
For more details on this algorithm please refer to the [metric vignette](http://htmlpreview.github.com/?https://github.com/TGuillerme/dispRity/blob/master/doc/dispRity-metrics.html).

@@

#### `sim.morpho`
This function (and it's associated utilities) allows to generate realistic discrete morphological matrices.
See the [associated vignette](http://htmlpreview.github.com/?https://github.com/TGuillerme/dispRity/blob/master/doc/dispRity-simulate_data.html) for more details.
